maxent model avec xvalidation (year-based test training)

### 2019-08-30 src/maxent_avec_xvalidation.Rmd

```{r avg asc layers cloglog}
clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)
stdep <- read.csv(paste0("../output/maxent/models/", timeslice, "/stack_depth.csv"), header = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(clogasc_list)){
    asc <- clogasc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
        colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "/cloglog_asclayerbydepth.csv")), row.names = TRUE)

>>>>

```{r avg asc layers cloglog}
mthna <- jul
timeslice <- jul
clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)
stdep <- read.csv(paste0("../output/maxent/models/", timeslice, "/stack_depth.csv"), header = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(clogasc_list)){
    asc <- clogasc_list[a]
    ascd <- str_sub(asc, 50, -5)
    if (grepl(dep, ascd)){
      depthlayers[d , paste0("a", colno)] <- asc
       colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "/cloglog_asclayerbydepth.csv")), row.names = TRUE)
